\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hariprasath Parthasarathy} & Email : \href{mailto:hariprasath95@gmail.com}{hariprasath95@gmail.com}\\
  \ &\ Mobile : +1-716-427-9783 \\

\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo(State University of New York)}{Buffalo, NY}
      {Master of Science in Computer Science and Engineering }{Aug. 2018 -- May. 2020}
      \begin{itemize}
        \item {{Coursework : Analysis of algorithms, Computer vision and image processing, operating systems.}} 
        \vspace{-5px}
      \end{itemize} 

    \resumeSubheading
      {Sri Ramakrishna Engineering College}{Coimbatore, India}
      {Bachelor of Engineering in Computer Science and Engineering.  }{Aug. 2013 -- July. 2017}


  \resumeSubHeadingListEnd
 

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Zoho Corporation}{Chennai, IN}
      {Member technical Staff - Zoho labs - Research and Development}{May 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{Cstore -FDW (Columnar  storages ,OLAP systems)}
          {    
            \resumeItemListStart
            \item{{Modified CITUSDB CStore FDW to accommodate in-memory caching, deletes and JIT executor.}}
            \item{{The JIT executor improved query performance by a factor of 8 - 10 on OLAP queries of 30 millions rows.}}
            \item{{Deployed Cstore system backing kafka/mysql across 30 clusters.}}
            \resumeItemListEnd
            }\vspace{2px}

               \resumeItemListEnd

      \resumeSubheading
        {Zoho Corporation}{Chennai, IN}
        {Member technical Staff Intern - Zoho labs - Research and Development}{Jan 2017 - Mar 2018}
        \resumeItemListStart
        \resumeItem{In Memory Foreign Data Wrapper For PostgreSQL (Database Design, C with LLVM, codegen API)}
        {
          \resumeItemListStart
            \item{{Designed and implemented the storage engine and executor as a foreign data wrapper for postgreSQL.}}
            \item{{Successfully implemented lock free indexing(BW tree) and write ahead logging.}}
            \resumeItemListEnd
        }  
        \resumeItemListEnd
        \resumeSubheading
      {Sri Ramakrishna Engineering College - Centre For Innovation }{Coimbatore, India}
      { Undergraduate Research / Student Chairman  }{Aug. 2015 -- Dec. 2016}
      \resumeItemListStart  
      \resumeItem{Fleet Management System -(Android,AngularJS-2,Redis,Embedded Systems)}  
        {
          \resumeItemListStart
          \item{{Led a team of 4 people to Design and implement hardware and software for the fleet management system.}}
          \item{{Detect irregular driving patterns and approximate time of arrival for institutional vehicles.}}
          \item{{Proved its commercial viability - And was Implemented for 50 vehicles for SNR Trust.}}
        \resumeItemListEnd
        }\vspace{2px}
        \resumeItem{Industrial Data Logging (Arduino, Mysql, PHP)}
        {
          \resumeItemListStart
          \item{ {A real time system used to extract production data from CNC machines. 
        It  aided proper planning and execution of orders in micro industries.
        }}
        \item{ {A pilot run of the project was executed in a padmabalaji spinners.
        }}
        \item{ {Won the best mini project award for its commercial viability and worker ease of use.}
        }
        \resumeItemListEnd
        }
        \resumeItemListEnd
        


  \resumeSubHeadingListEnd



% --------PROGRAMMING SKILLS------------
\section{Independent Projects}
\resumeSubHeadingListStart
\item{
  \textbf{{Health Fusion}}
\hfill
{September 2014 - June 2015}\\
  {Project based on Adhaar for safe Handling of medical data and preventing drug abuse }{}
   }  
\item{
  \textbf{{Faculty Assessment}}
\hfill
{May 2014 - July 2014}\\
  {Web Application for Faculty performance assessment based of student feedback}{}
   }
 

\resumeSubHeadingListEnd
% --------PROGRAMMING SKILLS------------
\section{Skills and Interest}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Profecient in C, C++, SQL, familiar with Android, Java ,Python, Javascript, LLVM-JIT, Perl}
    }
   \item{
    \textbf{Tools} GIT, Amazon web serivices, Linux, LAMP Stack.
  }
 \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Achievements}
\resumeSubHeadingListStart
\item{
{
  Industrial Datalogging was awarded the best Project of the term.
}}   
\item{
{Awarded \$14000 by SNR Trust for 'Vechicle Tracking System' For R\&D.}   
} 
\item{
{ Health Fusion was awarded as Innovative project award by HR Cube with an award of Rs:50000}}
   
 \resumeSubHeadingListEnd



% -------------------------------------------
\end{document}

