\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingItem}[2]{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hariprasath Parthasarathy} & Email : \href{mailto:hariprasath95@gmail.com}{hariprasath95@gmail.com}\\
  \ &\ Mobile : +1-916-430-6616 \\

\end{tabular*}


% --------PROGRAMMING SKILLS------------
\section{Skills and Interest}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, React, C, C++, Spring boot, Python, LLVM}
    }
   \item{
    \textbf{Interests}: Database Internals, Back-end development, Linux containers, Systems programming
  }
  \item{
    \textbf{Awards}: Won fastest query processor in CSE562, Best MS Researcher both from University at buffalo
  }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Oracle Corporation}{Redwood City, CA}
  {Senior database kernel engineer, Oracle DB }{June-2021 - current}
  \resumeItemListStart
    \resumeItem{Database sharding - native replication (C, C++, Raft consensus)}
      {    
        \resumeItemListStart
        \item{{writing / managing the IO and seriealization, coordination of shards for Raft based sharded database }}
       \resumeItemListEnd
        }\vspace{2px}

           \resumeItemListEnd
  \resumeSubheading
  {Amazon Services Inc}{Seattle, WA}
  {Software Development Engineer, Amazon Devices}{March 2020 - June 2021}
  \resumeItemListStart
    \resumeItem{Return processing and management for Amazon devices - (Java, Springboot, React))}
      {    
        \resumeItemListStart
        \item {{Responsible for redesigning and migrating an externally facing micro service containing 17 API’s optimizing
database fetches and API latency(average 20\% across all API’s)}}
        \item{{Deployed a new return workflow, which involved training workforce, debugging fixing release issues}}
        \resumeItemListEnd
        }\vspace{2px}

           \resumeItemListEnd
    \resumeSubheadingItem
  {Software Development Engineer Intern, Amazon Devices}{Summer 2019}
  \resumeItemListStart
    \resumeItem{Vision and Machine Learning based Screening- (Computer Vision, ML, Java, Spring, Angular)}
      {    
        \resumeItemListStart
        \item {{Tools to improve flow in warehouses. The tools created by me improved to rate of dispatches by 10\%}}
        \item{{Process return screening in warehouses with computer vision and machine learning. Accrately 92\%}}
        \resumeItemListEnd
        }\vspace{2px}

           \resumeItemListEnd
    \resumeSubheading
      {University at Buffalo}{Buffalo, NY}
      {Research Programmer - UB-ANC - Drones Lab}{Spring 2019}
      \resumeItemListStart
        \resumeItem{Drones navigation system - EMANE Integration (EMANE, NS3, LXC Containers)}
          {    
            \resumeItemListStart
            \item{{Modified UB's inhouse drone simulation to support AFRL's EMANE network simulator.}}
            \item{{Support integration with LXC containers that would facilitate Distributed simulation.}}
           \resumeItemListEnd
            }\vspace{2px}

               \resumeItemListEnd
        \resumeSubheading
      {Zoho Corporation}{Chennai, IN}
      {Member technical Staff - Zoho labs - Research and Development}{May 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{Cstore -FDW (Columnar  storages ,OLAP systems)}
          {    
            \resumeItemListStart
            \item{{Modified CITUSDB CStore FDW to accommodate in-memory caching, deletes and JIT executor.}}
            \item{{The JIT executor improved query performance by a factor of 8 - 10 on OLAP queries of 30 million rows.}}
            \item{{Deployed Cstore system backing kafka/mysql across 30 clusters.}}
            \resumeItemListEnd
            }\vspace{2px}

               \resumeItemListEnd
    \resumeSubheadingItem
        {Member Technical Staff Intern - Zoho labs - Research and Development}{Jan 2017 - Mar 2018}
        \resumeItemListStart
        \resumeItem{In Memory Foreign Data Wrapper For PostgreSQL (Database Design, C with LLVM, codegen API)}
        {
          \resumeItemListStart
            \item{{Designed and implemented the storage engine and executor as a foreign data wrapper for postgreSQL.}}
            \item{{Successfully implemented lock free indexing(BW tree) and write-ahead logging.}}
            \resumeItemListEnd
        }  
        \resumeItemListEnd
        \resumeSubheading
      {Sri Ramakrishna Engineering College - Centre For Innovation }{Coimbatore, India}
      { Undergraduate Research / Student Chairman  }{Aug. 2015 -- Dec. 2016}
      \resumeItemListStart  
      \resumeItem{Fleet Management System -(Android, AngularJS-2, Redis, Embedded C Programming)}  
        {
          \resumeItemListStart
          \item{{Led a team of 4 people to Design and implement hardware and software for the fleet management system.}}
          \item{{Detect irregular driving patterns and approximate time of arrival for institutional vehicles.}}
         \resumeItemListEnd
        }\vspace{2px}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo(State University of New York)}{Buffalo, NY}
      {Master of Science in Computer Science and Engineering }{Aug. 2018 -- Dec. 2019}
      \begin{itemize}
        \item {{Coursework: Analysis of algorithms, Computer vision and image processing, Operating systems, Distributed System, Database Systems, Malware Detection using static analysis}} 
        \vspace{-5px}
      \end{itemize} 
    \resumeSubheading
      {Sri Ramakrishna Engineering College}{Coimbatore, India}
      {Bachelor of Engineering in Computer Science and Engineering.  }{Aug. 2013 -- July. 2017}
  \resumeSubHeadingListEnd
\end{document}